HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-20 LaTeX/ms.tex
Hayward final comments

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~M.~Scudder\altaffilmark{3},
C.~Hayward\altaffilmark{4,5},
W.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
D.~Farrah\altaffilmark{11},
Hai~Fu\altaffilmark{12},
R.~Gavazzi\altaffilmark{13},
R.~Hopwood\altaffilmark{14},
R.~J.~Ivison\altaffilmark{15,16},
M.~Jarvis\altaffilmark{17},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{18,19},
D.~Rigopoulou\altaffilmark{20,21},
I.~G.~Roseboom\altaffilmark{3,16},
Douglas~Scott\altaffilmark{22},
A.~J.~Smith\altaffilmark{3},
J.~D.~Vieira\altaffilmark{23},
L.~Wang\altaffilmark{3},
J.~Wardlow\altaffilmark{24}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics, Virginia Tech, Blacksburg, VA 24061}
\altaffiltext{12}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{13}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{14}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{15}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

Halo catalogs are generated from the {\it Bolshoi} dark matter-only
cosmological simulation \citep{Klypin11} using the {\sc rockstar} halo finder
\citep{Behroozi13a,Behroozi13b}.  Catalogs of subhalos are created from eight
randomly chosen lightcones, each with an area of 1.4$^\circ \times 1.4^\circ$.
Galaxy properties such as stellar mass and SFR are assigned to the subhalos
using the abundance matching method of \citet{Behroozi13c}.  Dust masses are
assigned using an empirically determined redshift-dependent mass--metallicity
relation and an assumed dust-to-metal density ratio of 0.4 (see \citealt{HN13}
for details). Finally, submm flux densities are interpolated from the SFRs and
dust masses using a fitting function that is based on the results of dust
radiative transfer calculations performed on hydrodynamical simulations of
isolated and interacting galaxies \citep{H11,H12,HN13}.

@@

The \citet{HB13} model does not include SFR enhancements induced by starbursts
(see Section 4.5 of \citealt{HB13} for a detailed discussion of this
limitation). To explore whether interaction-induced starbursts are the origin
of the excess at small angular separations observed in our {\it Herschel}-ALMA
sample, we modified the \citet{HB13} model to include a crude treatment of
interaction-induced SFR enhancement. Mock galaxies with one or more neighbors
within a physical distance of 5$\,$kpc and with a stellar mass between
one-third and three times that of the galaxy under consideration (i.e.  a
`major merger') had their SFRs increased by a factor of two. For distances
smaller than 1$\,$kpc, the imposed increase was a factor of ten.  Because these
SFR enhancements are greater than suggested by simulations
\citep[e.g.][]{Cox08, H11, H14, Torrey12} or observations of local galaxy pairs
\citep[e.g.][]{Scudder12, Patton13}, we consider this test to provide an upper
limit on the possible effect of interactions on blended sources in the
\citet{HB13} model.  We find an insignificant effect on the values of $dN/dA$
when using the merger-induced model as described above.  The main reason for
this is that only two sources had their SFRs boosted by a factor of ten, and
$\approx150$ experienced a factor of two increase. In the \citet{HB13} model, a
factor of two increase in SFR corresponds to only a ~30\% increase in
$S_{870}$, so it is perhaps unsurprising that the weak boosts in SFR cause
little change in $dN/dA$.

@@

R.J.I. acknowledges support from European Research Council Advanced
Investigator Grant, Cosmicism, 321302.

>>>>

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~M.~Scudder\altaffilmark{3},
C.~C.~Hayward\altaffilmark{4,5},
W.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
D.~Farrah\altaffilmark{11},
Hai~Fu\altaffilmark{12},
R.~Gavazzi\altaffilmark{13},
R.~Hopwood\altaffilmark{14},
R.~J.~Ivison\altaffilmark{15,16},
M.~Jarvis\altaffilmark{17},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{18,19},
D.~Rigopoulou\altaffilmark{20,21},
I.~G.~Roseboom\altaffilmark{3,16},
Douglas~Scott\altaffilmark{22},
A.~J.~Smith\altaffilmark{3},
J.~D.~Vieira\altaffilmark{23},
L.~Wang\altaffilmark{3},
J.~Wardlow\altaffilmark{24}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics, Virginia Tech, Blacksburg, VA 24061}
\altaffiltext{12}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{13}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{14}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{15}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

Halo catalogs are generated from the {\it Bolshoi} dark matter-only
cosmological simulation \citep{Klypin11} using the {\sc rockstar} halo finder
\citep{Behroozi13a, Behroozi13b}.  Catalogs of subhalos are created from eight
randomly chosen lightcones, each with an area of 1.4$^\circ \times 1.4^\circ$.
Galaxy properties such as stellar mass and SFR are assigned to the subhalos
using the abundance matching method of \citet{Behroozi13c}.  Dust masses are
assigned using an empirically determined redshift-dependent mass--metallicity
relation and an assumed dust-to-metal density ratio of 0.4 (see \citealt{HN13}
for details). Finally, submm flux densities are interpolated from the SFRs and
dust masses using a fitting function that is based on the results of dust
radiative transfer calculations performed on hydrodynamical simulations of
isolated and interacting galaxies \citep{H11,H12,HN13}.

@@

The \citet{HB13} model does not include SFR enhancements induced by starbursts
(see Section 4.5 of \citealt{HB13} for a detailed discussion of this
limitation). To explore whether interaction-induced starbursts are the origin
of the excess at small angular separations observed in our {\it Herschel}-ALMA
sample, we analyzed modified versions of the \citet{HB13} model that include a
crude treatment of interaction-induced SFR enhancements \citep{Miller:2015lr}.
Mock galaxies with one or more neighbors within a physical distance of 5$\,$kpc
and with a stellar mass between one-third and three times that of the galaxy
under consideration (i.e.  a `major merger') had their SFRs increased by a
factor of two. For distances smaller than 1$\,$kpc, the imposed increase was a
factor of ten.  Because these SFR enhancements are greater than suggested by
simulations \citep[e.g.][]{Cox08, H11, H14, Torrey12} or observations of local
galaxy pairs \citep[e.g.][]{Scudder12, Patton13}, we consider this test to
provide an upper limit on the possible effect of interactions on blended
sources in the \citet{HB13} model, although the incompleteness of the
\citet{Behroozi13b} catalogs for mergers with small separations could cause
some interacting systems to be missed.  We find an insignificant effect on the
values of $dN/dA$ when using the merger-induced model as described above.  The
main reason for this is that only two sources had their SFRs boosted by a
factor of ten, and $\approx150$ experienced a factor of two increase. In the
\citet{HB13} model, a factor of two increase in SFR corresponds to only a ~30\%
increase in $S_{870}$, so it is perhaps unsurprising that the weak boosts in
SFR cause little change in $dN/dA$.

@@

R.J.I. acknowledges support from European Research Council Advanced
Investigator Grant, Cosmicism, 321302. C.C.H. is grateful to the Gordon and
Betty Moore Foundation for financial support.
